\begin{resumo}[Abstract]
\begin{otherlanguage*}{english}
The advancement of technology in recent years has caused a great impact on humanity. Nowadays it is almost inconceivable that there is any area that does not use the technology in some way. With this technological growth, it is essential to create means to ensure the safety of persons. Encryption has central importance in this context because it prevents confidential data from being disclosed by malicious people. But with the advancement in technology, the existing cryptographic systems require increasingly complex processing and to stay safe. Hence, it is necessary to seek alternatives to ensure the safety of individuals in the digital environment and using less computing resources. One such alternative is the use of elliptic curves in cryptography. This alternative offers the same security that encryption based on RSA, however, consuming far less computing resources. The security of elliptic curve cryptography is based on the difficulty in solving the discrete logarithm problem. However, there are some computational algorithms that solve this problem, which may compromise the security of cryptographic system. The objective of this study is to explore the key concepts that are used in interesting mathematical structure of elliptic curves and implementation of these attack algorithms, namely the Pollard-rho algorithm.

\vspace{\onelineskip}

\noindent 
\textbf{Key-words}: latex. abntex. text editoration.
\end{otherlanguage*}
\end{resumo}
